\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt plus 2pt minus 1pt}
}

\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\usepackage{hyperref}
\hypersetup{
            pdftitle={Dynamic Advertising for Supermarkets},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1.5cm, headsep=.2cm]{geometry}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\title{\vspace{-5ex}Dynamic Advertising for Supermarkets\vspace{-5ex}}\date{}

\begin{document}
\maketitle

We propose a platform to provide location based advertisements in a
shopping centre environment. Combining location data with users'
shopping profiles will enable more accurate and timely advertisements
for items nearby, as well as informing users of any coupons they may
have to use. Further, gathering the individual paths of the customers
will help in designing shop layout and future campaigns.

\hypertarget{prototype-design}{%
\section{Prototype Design}\label{prototype-design}}

For the initial prototype we will use an Android phone to provide the
interactive experience and to act as a communication gateway. A Nordic
nRF51-DK will be used to implement all other local functionality, and a
cloud service for data processing.

For a production solution human interaction will be via a low power
e-reader type screen integrated into the shopping trolley as well as
advertisement screens placed throughout the store. The nRF51-DK
localisation functionality will be integrated into the handheld
shop-as-you-go device. The handheld device will communicate through the
existing dedicated uplink and additionally deployed shared BLE gateways.

\hypertarget{implementation}{%
\section{Implementation}\label{implementation}}

The nRF51-DK will track BLE beacons placed throughout the store, as well
as integrating data from a multi-axis inertial movement sensor. This
data will be processed in a cloud service to identify the location of
the device. The location data will be gathered and stored for later
usage, and the current location (with relevant advertisements) will be
returned to the device.

\hypertarget{handheld-device}{%
\subsection{Handheld device}\label{handheld-device}}

\begin{itemize}
\tightlist
\item
  Identifies BLE beacons and their signal strength to triangulate
  location.
\item
  Records and transmit inertial movement data.
\item
  Manages its data storage, and if needed reduce recorded data
  granularity.
\item
  Continuously approximates location to display preconfigured
  advertisements.
\item
  Monitors its battery level and, in case of low battery, reduces
  communication frequency and processor load.
\item
  Ensures the handheld device remains functional for registering
  purchased items during a whole shopping session.
\item
  Connects to the cloud, using (in order of precedence) shared gateways
  and its own dedicated uplink.
\end{itemize}

\hypertarget{communication-gateway}{%
\subsection{Communication Gateway}\label{communication-gateway}}

For the prototype, the gateway will be implemented on the same mobile
phone as the phone app for user interaction. The gateway will connect to
the handheld device using BLE and relay data to a central processing hub
(cloud) via a Wi-Fi connection.

The devices and gateways will share a preconfigured set of keys to
encrypt data transmissions. These keys can be updated whenever the
devices are placed in a charging dock.

\hypertarget{mobile-application}{%
\subsection{Mobile application}\label{mobile-application}}

Android App is mainly made for customers, used for pushing notifications
and providing user's position in the store. Third party API and SDK,
preferably open source, will be used for visualising shopping cart's
position, map, items in promotion and push notifications.

For simplifying the prototype, the manager view will be alongside the
user view within the app. External tools will be used to visualise the
results of busiest area in the store and the effectiveness of targeted
marketing.

\hypertarget{cloud-services}{%
\subsection{Cloud Services}\label{cloud-services}}

\hypertarget{localisation}{%
\subsubsection{Localisation}\label{localisation}}

The cloud will receive, store and aggregate received data to identify
shoppers' locations. It will estimate the location of the handheld
devices by aggregating detected beacon signals and recorded inertial
movement sensor readings to reconstruct the path of the device
throughout the store.

\hypertarget{advertisement-delivery}{%
\subsubsection{Advertisement Delivery}\label{advertisement-delivery}}

As the display mechanism will be preloaded with advertisements, the
cloud will simply need to specify the ID of the desired ad. This will be
based on the shopping profile and current location. For user-specific
custom notifications, the system may deliver a full ad instead of using
the preconfigured set.

\hypertarget{data-analytics}{%
\subsubsection{Data Analytics}\label{data-analytics}}

Data collected such as duration at a sectional place will be used to
find the busiest area at a shop. This can be visualised via a heatmap on
the store map.

Sensor data from gyroscope, accelerometer and Bluetooth beacons can be
used to predict user's direction and position on a map.

The likelihood of the user going to the item after seeing the mobile
notifications can be analysed. This gives an insight of the marketing
effectiveness with regards to a user's characteristics and the marketed
items.

\hypertarget{evaluation-methodology}{%
\section{Evaluation methodology}\label{evaluation-methodology}}

\begin{description}
\hypertarget{location-accuracy}{%
\item[Location Accuracy]\label{location-accuracy}}
We will assess beacon, internal measurement, and combined sensor based
accuracy separately. Location accuracy metric will be the distance
between reported and actual coordinates on the map.

\hypertarget{power-consumption}{%
\item[Power Consumption]\label{power-consumption}}
The battery level and power draw will be measured during different
sleep-wake patterns of the board. We will calculate the effects of
various optimisations on estimated battery life.

\hypertarget{responsiveness}{%
\item[Responsiveness]\label{responsiveness}}
Most factors that determine the responsiveness are external and cannot
be controlled. For example, current gateway traffic and BLE to phone
responsiveness, shared gateway availability in current location.
However, this can be simulated and the delay in user's location update
on the map can be measured to assess resilience to adverse effects.
\end{description}

\hypertarget{limitations}{%
\section{Limitations}\label{limitations}}

Given the small form factor battery powered nature of the platform, we
will need to be conscious of power usage. Fortunately the devices will
need to last for a single shopping journey, and can be recharged before
the next user will use it.

Care will need to be taken to ensure the privacy of the customers and to
not leak their shopper profiles. This applies both to communications and
the ads displayed locally and publicly. Advertisement content related
privacy concerns are out of scope for this platform.

\end{document}
